---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# The `nos` R package
[![CRAN Downloads](http://cranlogs.r-pkg.org/badges/grand-total/nos)](https://cran.r-project.org/package=nos)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/nos)](https://cran.r-project.org/package=nos)
[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-yellow.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![CircleCI](https://circleci.com/gh/txm676/nos/tree/master.svg?style=svg)](https://app.circleci.com/pipelines/github/txm676/nos?branch=master)


Calculate NOS (node overlap and segregation) and the associated metrics
described in Strona and Veech (2015) <DOI:10.1111/2041-210X.12395> and Strona et
al. (2017; In Press, DOI to be provided in subsequent package version). The
functions provided in the package enable assessment of structural patterns
ranging from complete node segregation to perfect nestedness in a variety of
network types. In addition, they provide a measure of network modularity.

The package is currently on CRAN and can be installed via

```{r eval=FALSE}
install.packages("nos")
```

Alternatively, you can install the developmental version via

```{r eval=FALSE}
devtools::install_github("txm676/nos")
```
